Cannibalism among the supermassive black holes

### 2016-08-26 paper.tex
added new plots of radii over time

\section{Results}\label{sec:results}
\begin{figure*}[htbp]
\begin{center}
\includegraphics[width=0.45\textwidth]{plots/orbiting_bh_mass_histogram_gal_1.png}
\includegraphics[width=0.45\textwidth]{plots/orbiting_bh_mass_histogram_gal_65.png}\\
\includegraphics[width=0.45\textwidth]{plots/orbiting_bh_mass_histogram_gal_187.png}
\includegraphics[width=0.45\textwidth]{plots/orbiting_bh_mass_histogram_gal_217.png}\\
\caption{default}
\label{default}
\end{center}
\end{figure*}

\subsection{Mergers}

\subsection{Ejections}

\subsection{Stalling SMBH binaries}

@@

>>>>

Note: we only inject the BHs into the simulation that have a $t_{fric}$ smaller than 100 times the Hubble time.

\section{Results}\label{sec:results}
\begin{figure*}[htbp]
\begin{center}
\includegraphics[width=0.45\textwidth]{plots/radius_A.png}
\includegraphics[width=0.45\textwidth]{plots/radius_B.png}\\
\includegraphics[width=0.45\textwidth]{plots/radius_C.png}
\includegraphics[width=0.45\textwidth]{plots/radius_D.png}\\
\caption{default}
\label{default}
\end{center}
\end{figure*}

\begin{figure*}[htbp]
\begin{center}
\includegraphics[width=0.45\textwidth]{plots/orbiting_bh_mass_histogram_gal_1.png}
\includegraphics[width=0.45\textwidth]{plots/orbiting_bh_mass_histogram_gal_65.png}\\
\includegraphics[width=0.45\textwidth]{plots/orbiting_bh_mass_histogram_gal_187.png}
\includegraphics[width=0.45\textwidth]{plots/orbiting_bh_mass_histogram_gal_217.png}\\
\caption{default}
\label{default}
\end{center}
\end{figure*}

\subsection{Mergers}
\noindent A: two mergers early on, and then two more at around 10-12 Gyr\\
B: 4 mergers across the final 8 Gyr\\
C: two mergers in the final Gyrs\\
D: ?\\

\subsection{Ejections}
No complete ejections, but kicks to higher energy orbits.
\noindent A: one in a three-body encoutner\\
B: 7-ish kicks, some in nearly 4-body encounters\\
C: none\\
D: ?\\

\subsection{Stalling SMBH binaries}
A: two periods of BH binary in center for > Gyr, up to 6 Gyr\\
B: two short periods of BHBs\\
C: 2 classic BHB periods of about 1 Gyr each\\
D: ?

@@

A: 95\% never make it into the central kpc\\
B: still about 90\% are in the halo\\
C: \\
D: ?
